\documentclass[a4paper]{article}
\usepackage{enumitem}

%opening
\title{\vspace{-2cm}ENGG4810 Team 26\\
	Code of Conduct and Code of Ethics\vspace{1cm}}
\author{Ryan Fitzimon\\
	43214907\\
	\texttt{ryan.fitzsimon@uq.net.au}
	\and
	Minh Toan Ho\\
	43129560\\
	\texttt{minh.ho2@uq.net.au}
	\and
	Christopher Low\\
	42897367\\
	\texttt{christopher.low@uq.net.au}
	\and
	Joshua Mason\\
	43237746\\
	\texttt{joshua.mason1@uq.net.au}
	\vspace{1cm}
}

\begin{document}

\maketitle
\vspace{1cm}

\section{Code of Ethics}
We, the members of Team 26, hereby agree:
\begin{enumerate}
	\item to treat one another with respect;
	\item to be trustworthy, honest and reliable;
	\item to be prompt, transparent and realistic in our communication of progress, issues and concerns;
	\item to offer and accept genuine criticism of each other's work, and to properly give credit where it is due;
	\item to perform to the best of our ability;
	\item to identify hazards and implement appropriate risk mitigation measures before undertaking any activity; and
	\item to assist one another with our tasks and support each other in following this code of ethics.
\end{enumerate}

\pagebreak
\section{Code of Conduct}

\subsection{Safety}
\begin{enumerate}[label=(\alph*)]
	\item Before undertaking any activity, potential hazards should be identified and appropriate measures implemented to mitigate risks.
	\item Team members should inform each other of any hazards encountered, especially before accepting assistance with an activity.
	\item Full compliance with UQ OH\&S procedures is required.
\end{enumerate}

\subsection{Personal Conduct}
\begin{enumerate}[label=(\alph*)]
	\item Team members will treat one another with respect at all times.
	\item Genuine criticism of work is encouraged. Whilst personal attacks are unacceptable, criticism should be delivered in a direct and honest manner, even if this risks damaging another team member's pride.
	
\end{enumerate}

\subsection{Communication}
\begin{enumerate}[label=(\alph*)]
	\item Formal meetings will be held weekly. Attendance is required for all team members. If a team member is unable to attend, they should notify the rest of the team in advance and make an effort to catch up on any developments.
	\item Concerns regarding the performance of or progress made by other team members should be raised at team meetings in a prompt and professional manner. Tutors or coordinators should be contacted for any further issues.
	\item Other than face-to-face conversation, the primary means of communication will be a Slack team. It is expected that all team members will regularly contribute to discussion in the appropriate Slack channels. In urgent situations, phone calls will be made, but this is not preferred due to the lack of records.
	\item Team members should remain contactable for the duration of the project. If a team member expects to be uncontactable for more than 24 hours the team should be notified in advance.

\end{enumerate}

\subsection{Management Process}
\begin{enumerate}[label=(\alph*)]
	\item Each team member will be appointed as the lead for an aspect of the project. They will be expected to ensure that sufficient progress is made in this area and will provide updates on any developments at each team meeting. 
\end{enumerate}

\subsection{Work Performance}
\begin{enumerate}[label=(\alph*)]
	\item If a team member believes that they may be unable to meet a deadline, the team should be notified as soon as possible.
	\item Any issues or problems arising which may impede progress should be brought up with the team as soon as possible for the team to solve or request help on. It is the responsibility of the whole team to help with issues that one member cannot overcome. Team members should be transparent with any problems or concerns in their work.
\end{enumerate}

\subsection{Source Code Control}
\begin{enumerate}[label=(\alph*)]
	\item All source code for documents and programs will be stored in a single Git repository.
	\item Commits should be focused. Each issue fixed and feature implemented should have a separate commit.
	\item Commit messages should be concise and informative. Messages such as "Bug fixes" are unacceptable.
	\item The master branch should always be compilable. Features that are likely to break should  be implemented in separate branches and merged upon completion.
\end{enumerate}

\subsection{Budget}
\begin{enumerate}[label=(\alph*)]
	\item A single team member will be appointed to make all purchases and keep the BOM updated. This person will collect the entire reimbursement at the conclusion of the project.
	\item Consensus will be reached before the purchase of all items. If a team member fails to respond to a request for input within 24 hours, their vote will be forfeited.
\end{enumerate}

\end{document}
